---
title: "Homework 5"
output: github_document
---

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)


knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```



```{r}
library(tidyverse)
library(readr)
library(ggplot2)
library(dplyr)
library(broom)
```

# Question 1

# Question 2
Import and tidy data
```{r}

file_path = list.files(path = "data", pattern = "\\.csv$", full.names = TRUE)

study_df=
  file_path |> as.data.frame() |> mutate(data=map(file_path,read_csv)) |> as.tibble() |> unnest(data) |> 
mutate(
  file_path=str_replace(file_path,'\\.csv', ''),
  file_path=str_replace(file_path, 'data/','')
) |> 
    janitor::clean_names() |> 
    pivot_longer(
    week_1:week_8,
    names_to = "week", 
    values_to = "observations",
    names_prefix = "week_")|> 
    separate(file_path,into = c("arm","subject_id"))


```

Spaghetti Plot
```{r}
spaghetti_plot =
  study_df |> 
  ggplot(aes(x= week, y=observations, group=subject_id, color=subject_id))+geom_line()+
  facet_grid(~arm)+
    labs(title = "Spaghetti Plot of Observations Over Time",
       x = "Week",
       y = "Observations",
       color = "subject_id")

spaghetti_plot
```
Comments: Compare these two spaghetti plots group by arm, we can see that the 
control arm has the range of observations between around -2.45 and 4.25, however
the experimental arm has the range of observations between around -1.45 and 7.50,
which is more higher and larger range than the control arm.

# Question 3
Create dataset
```{r}
set.seed(12345)

sim_df = function(mu,n=30,sigma=5) {
  data =rnorm(n=30, mean = mu, sd=sigma)
  p_value=t.test(data, mu=0 ,alpha = 0.05)
  p_value |> 
    broom::tidy() |> 
    select(estimate, p.value)
}

sim_results_df= map(1:5000,\(i) sim_df(mu=0))|> bind_rows()

```


## Making plots with conditions of μ={1,2,3,4,5,6}
```{r}
mu_result_df = 
  expand_grid(
    mu = c(1:6),
    iter = 1:5000
  ) |> 
  mutate(estimate = map(mu, sim_df)) |> unnest(estimate) |> 
  mutate(power=p.value<0.05)

```

